---
title: "Analysis with R"
author: Y3926947
format: html
editor: visual
---

### Import Tidyverse library.
#### Turb off warnings

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```


```{r}
library(tidyverse)
```

### Load the data which is in CSV format and save to variable 'data'.

```{r}
data <- read_csv("data.raw.csv", show_col_types = FALSE)
```

# **Exploratory Analysis**

## Step 1.

### Observe total number of survey taken.

```{r}
data |>
  group_by(ID) |>
  count()
```

### Obtain the mean age.

```{r}
data |>
    summarise(mean = mean(Age))
```

### Check the relationship between 'BMI' and 'Physical activeness' and visualize observation.

#### Replace NA values with the mean of the 'Physical Activeness' and 'BMI' columns.

```{r}
phys_mean  <- data |>
  summarise(mean = mean(PhysActiveDays))
```

```{r}
bmi_mean  <- data |>
  summarise(mean = mean(BMI))
```

```{r}
data["PhysActiveDays"][is.na(data["PhysActiveDays"])] <- 2

```

### Observe total number of survey taken by each 'Sex (Male and Female)'.

```{r}
data["BMI"][is.na(data["BMI"])] <- 29
```

```{r}
data |>
  group_by(Sex) |>
  count()
```

### Explore the mean of the 'Physical Active days' and use to create a condition.

```{r}
data |>
  summarise(mean = mean(PhysActiveDays))
```

### Create a new column using condition to categorize 'Physical Activeness' into 'Barely active' and 'Active'.

```{r}
data$activeness <- with(data, ifelse(PhysActiveDays > 2.9, 'Active', 'Barely Active'))
```

### Plot 'Activeness' against 'BMI' and filter with 'Sex'.

#### Visualize.

```{r}
#| fig-cap: "Physical Activeness against BMi, filtered with Gender"
ggplot(data, aes(x = activeness, y = BMI, fill=Sex)) + stat_summary(fun=mean, geom = 'bar')
```

# Exploratory Analysis 2

#### Observe the relationship between 'Weight' and 'BMI'.

#### First evaluate mean of Weight.

```{r}
data |>
  summarise(mean = mean(Weight))
```

#### Create a new column using condition to categorize 'Weight' into 'Over_weight', 'Average Weight'.

```{r}
data$over_weight <- with(data, ifelse(Weight > 83.4, 'Overweight', 'Average weight'))
```

#### Plot 'Over_weight', and 'BMI' and observe.

```{r}
#| fig-cap: "Weight against BMI"
ggplot(data, aes(x = over_weight, y = BMI)) +  geom_boxplot()
```

# Exploratory Analysis 3

### Observe the weight of smokers. Most especially if smoking at an early age increases the tendency to be an averagely weighed person.

#### Fill NA values with value of the mean of column 'Smoke Age'.

```{r}
smokeage_mean  <- data |>
  summarise(mean = mean(SmokeAge))
```

```{r}
data["SmokeAge"][is.na(data["SmokeAge"])] <- 7
```

```{r}
#| fig-cap: "Weight against Age"
ggplot(data, aes(x = over_weight, y = SmokeAge)) +  geom_boxplot()
```

# Hypothesis

#### To test if the 'Pulse pressure' increase with 'Age.

## Using a Two-way Anova test for the group column ['Male and 'Female\] against 'Pulse Pressure'.

### Run Two-way Anova.

```{r}
mod <- aov(Pulse ~ Sex, data = data)
summary(mod)
```

### Print Model and observe correlation. Make conclusion.

```{r}
summary(mod)
```

### Visualize

```{r}
ggplot(data = data) +
  aes(x = Sex, y = Pulse) +
  geom_boxplot()
```

# Hypothesis 2

### To check the tendency that older smokers are diabetic.

## Run Chi-test.

### Best used for categorical data having multiple decisions.

```{r}
mod2 <- chisq.test(data$SmokeNow, data$Diabetes, correct=FALSE)
```

### Print Model and observe correlation. Make conclusion.

```{r}
summary(mod2)  
```

### Visualize and observe old people still smoke or quit.

```{r}
#| fig-cap: "Current Smokers Against Diabetes record"
ggplot(data) + geom_point(mapping =aes(x= SmokeNow, y=SmokeAge))
```

## Hypothesis 3

### Further drill the 'women' data set. To observe if elderly women are more overweight and at what age they tend to weigh most.

### Filter to only display women older than 45, these set of Women would be considered to be elderly,

```{r}
women <- filter(data, Sex == 'female')
```

```{r}
old_women <- filter(women, Age > 45)
```

### Run Linear Model to check correlation.

```{r}
mod3 <- lm(data = old_women,
          Age ~ Weight)
```

### Print Model and observe correlation. Make conclusion.

```{r}
summary(mod3)   
```

### Visualize

```{r}
#| fig-cap: "Age of Eldery Women against Weight"
ggplot(old_women,aes(x=Age,fill=Weight))+
  geom_histogram(position="dodge",binwidth=5)+theme_bw()
```

## End of Analysis

### Present results and Observation in PDF Doc.

#### Save Tables as a CSV file

```{r}
library( broom )
write.csv( tidy( mod ) , "coefs.csv" )
write.csv( glance( mod ) , "an.csv" )

write.csv( tidy( mod2 ) , "coefs2.csv" )
write.csv( glance( mod2 ) , "an.csv" )

write.csv( tidy( mod3 ) , "coefs3.csv" )
write.csv( glance( mod3 ) , "an.csv" )
```
